Designing Types for R, Empirically

### 2020-05-15 paper/main.tex
Add some numbers

<<Insert proportion of monorphic types in argument and in function
signature. Perhaps a table of monomorphic type signatures that are
popular...>>

@@

We observe that XXX of the positions have a single type ascribed to them,
and, only XXX have four or more types ascribed to them. Parameter PARAMNAME
of function XXXXCOLONCOLONXXX has the maximum, XXX, types ascribed to it.
Hence, most functions admit or return a uni-typed value.

@@

>>>>

@@

There are \PercUnitypedPositions monomorphic parameter and return value
positions in function signatures. Only \PercManytypedPositions positions have
four or more types ascribed to them. Parameter PARAMNAME of function
XXXXCOLONCOLONXXX has the maximum, XXX, types ascribed to it. Most functions
admit or return a uni-typed value.

@@

We observe that XXX of the positions have a single type ascribed to them, and,
only XXX have four or more types ascribed to them.
